---
title       : Life Expectancy Analysis
subtitle    : 
author      : ZAW HTET WAI
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, shiny, interactive, bootstrap}
ext_widgets : {rCharts: ["libraries/nvd3"]}
mode        : selfcontained # {standalone, draft}
---

```{r setup, message = F, echo = F}
require(rCharts)
options(RCHART_WIDTH = 800, RCHART_HEIGHT = 400, rcharts.mode = 'iframe', rcharts.cdn = TRUE)
knitr::opts_chunk$set(comment = NA, tidy = F, message = F)
```


## Background

 - To give insight on life expectancy of all countries over the world from year 1990 to 2012.
 - Data are obtained from from the <b>Global Health Observatory (GHO)</b>.
 - Source: http://apps.who.int/gho/data/node.main.3?lang=en
 - For Self-Service App: https://zawhtet.shinyapps.io/LifeExp

---

## Preparation
- Data are cleansed and formatted as 2 sets.
- One for at birth and another for at age 60.

```{r, echo=FALSE, warning=FALSE}
source("data_process.R")
birth_exp <- load_birth_exp()
sixty_exp <- load_sixty_exp()
head(birth_exp, 5)
head(sixty_exp, 5)
```

---

## Life Expectancy Analysis at Birth
- South Africa (1990-2012)

```{r results = 'asis', message = F, echo = F}
source("data_process.R")
birth_exp <- load_birth_exp()
selected <- 'South Africa'
    birth_exp_country <- subset(birth_exp, Country == selected & Year %in% seq(1990, 2012, 1))
    h1 <- hPlot(
      x = "Year", 
      y = "lex", 
      group = "Gender", 
      data = birth_exp_country, 
      type = "line")

    h1$colors(c("red", "blue"))
    h1$yAxis(title = list(enabled = TRUE, text = 'Life Expectancy at Birth'))
    h1$show('iframesrc', cdn  = TRUE)
```

---

## Life Expectancy Analysis at Age 60
- South Africa (1990-2012)

```{r results = 'asis', message = F, echo = F}
source("data_process.R")
sixty_exp <- load_sixty_exp()
selected <- 'South Africa'
    sixty_exp_country <- subset(sixty_exp, Country == selected & Year %in% seq(1990, 2012, 1))
    h2 <- hPlot(
      x = "Year", 
      y = "lex", 
      group = "Gender", 
      data = sixty_exp_country, 
      type = "line")

    h2$colors(c("orange", "green"))
    h2$yAxis(title = list(enabled = TRUE, text = 'Life Expectancy at 60'))
    h2$show('iframesrc', cdn = TRUE)

```
